---
title: "Using ComplementDNASeq"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using ComplementDNASeq}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

`ComplementDNASeq` provides a simple utility to compute the reverse complement of DNA sequences. This vignette walks through typical usage patterns and discusses how the package validates input.

## Installation

The package can be installed from GitHub using `remotes`:

```{r eval = FALSE}
# install.packages("remotes")
remotes::install_github("CEDRICHK/ComplementDNASeq")
```

## Basic usage

Load the package and call `reverse_complement()` with a DNA sequence composed of `A`, `C`, `G`, and `T`.

```{r}
library(ComplementDNASeq)
reverse_complement("GATTACA")
```

The function returns the reverse complement sequence, flipping the order and swapping each nucleotide with its complement (`A` ↔ `T`, `C` ↔ `G`).

## Handling invalid input

If the input contains characters other than the standard nucleotides, the function raises an error to prevent ambiguous results.

```{r, error = TRUE}
reverse_complement("GATUACA")
```

Missing values are propagated unchanged so that the function can be safely used on vectors that may contain `NA` entries.

```{r}
reverse_complement(NA_character_)
```

## Working with vectors

`reverse_complement()` operates on a single sequence at a time. When you have a vector of sequences, combine it with vectorised helpers such as `vapply()`.

```{r}
seqs <- c("ACTG", "TTTT", "CGCG")
vapply(seqs, reverse_complement, character(1))
```

The helper ensures each element is processed individually while returning a character vector of matching length.
